Missing links and the topological robustness of food webs

### 2023-05-26 manuscript/ms_C3_v3.Rmd
Updated ms, SI

 1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food webs. Undersampling can be compensated for by using food web models such as the allometric diet breadth model (ADBM) to predict missing links. Simultaneously, models might predict links which cannot occur, i.e., real false positives. 
  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than observed ones. Thus, we expect that predicted food webs are more robust than the observed ones. However, this expectation has never, to our knowledge, been tested, nor has the effect size, i.e. the difference in robustness of predicted and observed food web with respect to the difference in their connectance, been quantified.
  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links. We did this for 12 different food webs from a wide variety of ecosystems. We used three extinction scenarios: random, most connected, and least connected.
  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, which can be attributed to the higher connectance of the predicted food webs. On average, for every one unit of increase in connectance, we found that the food webs robustness increased by 0.52 units for the most connected species extinction scenario and by 0.04 units for the random species extinction scenarios. On the other hand, we saw no effect or very little effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
  5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models. Also, the differences in the structural properties of the model predicted food webs and the observed food webs suggest structural properties of a food web could be used as summary statistics to fit models such as the ADBM to the observed data.

@@

## Paragraph on how other structural food web properties are responsible as well

@@

A key assumption of the observed food webs is that they are very well sampled, i.e. all the links that in reality can occur are represented. However, it is known that not all food webs are very well sampled and do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016]. Some rare trophic links require more sampling effort than others, whereas some trophic links (sometimes referred to as forbidden links) remain unobserved because of biological constraints such as spatio-temporal uncoupling, size or reward mismatching, foraging constraints and physiological-biochemical constraints, which are irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016]. Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones. One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008] (reference (gut content paper)) to predict the missing links and then measure the robustness of the predicted food web. The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare. However, this solution is not infallible, as it is likely that the food web model might still miss some links and also may predict some links that could not, in fact occur.

@@

The food webs were more robust to the random extinction scenario than the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had more variations in robustness within the model food webs as compared to the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond and Broadstone Stream (taxonomic aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs. The food webs were more robust to the random extinction scenario than the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had more variations in robustness within the model food webs as compared to the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs. Although there were few less robust model food webs in the Broadstone Stream (size aggregation) as shown by the outliers.

@@

```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. Some points are not visible due to perfect overlap in b and c. Refer to Fig. 7 in the Supplementary Information for a faceted visualisation. The dashed black lines are the 1:1 relationships for reference."}
knitr::include_graphics("../results/plot_R50_ADBM_vs_obs.png")
```

@@

## A paragraph on the implication of our study

* On the uncertainty in the ADBM estimates 
* On the limitation of a food web model 
* On undersampling

Our study also depicts that the uncertainty in the model predictions can have a strong influence on the perceived robustness of the observed food webs. The large variations in the robustness of the model predicted food webs suggest why it is crucial to incorporate uncertainty in the food web predictions. At the same time, our study also quantifies the impact of undersampling on the perceived robustness of the observed food webs which then influences the perceived functioning and stability of the food webs (reference). This strongly suggest why it is crucial to incorporate the influence of undersampling.

Contrary to general expectations [@dunneNetworkStructureBiodiversity2002], food web robustness did not always increase with the connectance (Fig. \ref{fig:fig_r5}). For example, the Benguela Pelagic and Small Reef ADBM predicted food webs were surprisingly less robust to primary extinctions on average in the least connected extinction scenario compared to the observed food webs (Fig. \ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)). In these two food webs, the extinction of the least connected species could cause an almost complete, or complete collapse of the food web. We suspect this is because the ADBM predicted food webs have a lower proportion of basal species when compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022). As a result, these low-degree basal species are the ones to be removed at an early stage in the deletion sequence, thereby resulting in an earlier food web collapse in the ADBM predicted food web as compared to that of the observed food web (Fig: \ref{fig:fig_r3} (a) and (j)). This suggests that the greater connectance predicted by the ADBM resulted in a more robust food web on average. However, differences in the predicted food web properties, such as a lower proportion of basal species and higher maximum trophic level (Fig: \ref{fig:fig_a1}) when compared to that of the predicted food webs counteracted that effect and led to reduced robustness. On average, a consumer in a food web with a higher maximum trophic level would have fewer resources and be more susceptible to extinction than a consumer in a food web with a lower maximum trophic level [@binzerSusceptibilitySpeciesExtinctions2011]. This suggests that food web properties other than connectance play an important role in determining a food web's robustness and, therefore, should also be taken into account [@binzerSusceptibilitySpeciesExtinctions2011; @mendoncaRobustnessTemperateTropical2022; @riedeSizebasedFoodWeb2011].

@@

Since the ADBM predicted food webs have a lower proportion of basal species and a higher maximum trophic level as compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022 and Fig. \ref{fig:fig_a1} in Supplementary Information), it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs. We would expect a more highly constrained predicted food web structure, lower variation in robustness, and a greater apparent influence of connectance on robustness.

@@

# Supplementary Information

```{r, echo=FALSE, fig.align='center', fig.pos="H", out.width="450px", fig.cap="\\label{fig:fig_a1} The maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs. Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. The dashed black lines are the 1:1 relationships for reference."}
knitr::include_graphics("../results/plot_max_tl_ADBM_vs_emp.png")
```

```{r, echo=FALSE, fig.align='center', fig.pos="H", out.width="450px", fig.cap="\\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. The dashed black lines are the 1:1 relationships for reference."}
knitr::include_graphics("../results/plot_R50_ADBM_vs_obs_ra_lc_facet.png")
```

>>>>

 1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food webs. Undersampling can be compensated for by using food web models such as the allometric diet breadth model (ADBM) to predict missing links. Simultaneously, models might predict links which cannot occur, i.e., real false positives. 
  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than the observed ones. Thus, we expect that predicted food webs are more robust than the observed ones. However, this expectation has never, to our knowledge, been tested, nor has the effect size, i.e. the difference in robustness of predicted and observed food web with respect to the difference in their connectance, been quantified.
  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links. We did this for 12 different food webs from a wide variety of ecosystems. We used three extinction scenarios: random, most connected, and least connected.
  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, which can be attributed to the higher connectance of the predicted food webs. On average, for every one unit of increase in connectance, we found that the food webs robustness increased by 0.52 units for the most connected species extinction scenario and by 0.04 units for the random species extinction scenarios. On the other hand, we saw no effect or very little effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
  5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models. Also, the differences in the structural properties of the model predicted food webs and the observed food webs suggest structural properties of a food web could be used as summary statistics to fit models such as the ADBM to the observed data.

@@

<!-- ## Paragraph on how other structural food web properties are responsible as well -->

@@

A key assumption of the observed food webs is that they are very well sampled, i.e. all the links that in reality can occur are represented. However, it is known that not all food webs are very well sampled and do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016]. Some rare trophic links require more sampling effort than others, whereas some trophic links (sometimes referred to as forbidden links) remain unobserved because of biological constraints such as spatio-temporal uncoupling, size or reward mismatching, foraging constraints and physiological-biochemical constraints, which are irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016]. Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones. One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008; @gupta2023many] to predict the missing links and then measure the robustness of the predicted food web. The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare. However, this solution is not infallible, as it is likely that the food web model might still miss some links and also may predict some links that could not, in fact occur.

@@

The food webs were more robust to the random extinction scenario than the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had more variations in robustness within the model food webs as compared to the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs (Fig. \ref{fig:fig_r4} (b)). Although there were few less robust model food webs in the Broadstone Stream (size aggregation) as shown by the outliers.

@@

```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. Some points are not visible due to perfect overlap in b and c. Refer to Fig. S3 in the Supplementary Information for a faceted visualisation. The dashed black lines are the 1:1 relationships for reference."}
knitr::include_graphics("../results/plot_R50_ADBM_vs_obs.png")
```

@@

Our study also depicts that the uncertainty in the model predictions can have a strong influence on the perceived robustness of the observed food webs. The large variations in the robustness of the model predicted food webs suggest why it is crucial to incorporate uncertainty in the food web predictions. At the same time, our study also quantifies the impact of undersampling on the perceived robustness of the observed food webs which then influences the perceived functioning and stability of the food webs [@thompson2012food; @dunne2002network]. This strongly suggest why it is crucial to incorporate the influence of undersampling.

Contrary to general expectations [@dunneNetworkStructureBiodiversity2002], food web robustness did not always increase with the connectance (Fig. \ref{fig:fig_r5}). For example, the Benguela Pelagic and Small Reef ADBM predicted food webs were surprisingly less robust to primary extinctions on average in the least connected extinction scenario compared to the observed food webs (Fig. \ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)). In these two food webs, the extinction of the least connected species could cause an almost complete, or complete collapse of the food web. We suspect this is because the ADBM predicted food webs have a lower proportion of basal species when compared to that of the observed food webs (Fig. 6 (a) in @guptaSimultaneouslyEstimatingFood2022). As a result, these low-degree basal species are the ones to be removed at an early stage in the deletion sequence, thereby resulting in an earlier food web collapse in the ADBM predicted food web as compared to that of the observed food web (Fig. S1 (a) and (j) in the Supplementary Information). This suggests that the greater connectance predicted by the ADBM resulted in a more robust food web on average. However, differences in the predicted food web properties, such as a lower proportion of basal species (Fig. 6 (a) in @guptaSimultaneouslyEstimatingFood2022) and higher maximum trophic level (Fig. S2 in the Supplementary Information) when compared to that of the predicted food webs counteracted that effect and led to reduced robustness. On average, a consumer in a food web with a higher maximum trophic level would have fewer resources and be more susceptible to extinction than a consumer in a food web with a lower maximum trophic level [@binzerSusceptibilitySpeciesExtinctions2011]. This suggests that food web properties other than connectance play an important role in determining a food web's robustness and, therefore, should also be taken into account [@binzerSusceptibilitySpeciesExtinctions2011; @mendoncaRobustnessTemperateTropical2022; @riedeSizebasedFoodWeb2011].

@@

Since the ADBM predicted food webs have a lower proportion of basal species and a higher maximum trophic level as compared to that of the observed food webs (Fig. 6 (a) in @guptaSimultaneouslyEstimatingFood2022 and Fig. S2 in the Supplementary Information), it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs. We would expect a more highly constrained predicted food web structure, lower variation in robustness, and a greater apparent influence of connectance on robustness.

@@

### 2023-05-26 manuscript/ms_C3_v3.tex
Updated ms, SI

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Undersampling can lead to missing trophic interactions in recorded
  food webs, with potential consequences for the perceived functioning
  and stability of the food webs. Undersampling can be compensated for
  by using food web models such as the allometric diet breadth model
  (ADBM) to predict missing links. Simultaneously, models might predict
  links which cannot occur, i.e., real false positives.
\item
  Previous research shows that (i) food web robustness (the inverse of
  the number of secondary extinctions occurring due to primary
  extinctions) increases with connectance (the number of realised
  trophic links divided by the number of possible links), and (ii) that
  model predicted food webs usually have greater connectance than
  observed ones. Thus, we expect that predicted food webs are more
  robust than the observed ones. However, this expectation has never, to
  our knowledge, been tested, nor has the effect size, i.e.~the
  difference in robustness of predicted and observed food web with
  respect to the difference in their connectance, been quantified.
\item
  We fill this research gap by comparing the robustness of observed food
  webs to the robustness of food webs predicted by a model (the ADBM)
  that can account for missing links. We did this for 12 different food
  webs from a wide variety of ecosystems. We used three extinction
  scenarios: random, most connected, and least connected.
\item
  We found, as expected, that the predicted food webs were more robust
  than the observed food webs, which can be attributed to the higher
  connectance of the predicted food webs. On average, for every one unit
  of increase in connectance, we found that the food webs robustness
  increased by 0.52 units for the most connected species extinction
  scenario and by 0.04 units for the random species extinction
  scenarios. On the other hand, we saw no effect or very little effect,
  on average, of increased connectance for the least connected species
  extinction scenario for all except two of the 12 food webs.
\item
  These results show that undersampling can lead to large underestimates
  of food web robustness that can be compensated for by filling in
  missing links with food web models. Also, the differences in the
  structural properties of the model predicted food webs and the
  observed food webs suggest structural properties of a food web could
  be used as summary statistics to fit models such as the ADBM to the
  observed data.
\end{enumerate}
\end{abstract}

@@

\hypertarget{paragraph-on-how-other-structural-food-web-properties-are-responsible-as-well}{%
\subsection{Paragraph on how other structural food web properties are
responsible as
well}\label{paragraph-on-how-other-structural-food-web-properties-are-responsible-as-well}}

@@

A key assumption of the observed food webs is that they are very well
sampled, i.e.~all the links that in reality can occur are represented.
However, it is known that not all food webs are very well sampled and do
not represent all of the feeding links that can occur (Caron et al.,
2022; Jordano, 2016; Patonai \& Jord'an, 2017). Some rare trophic links
require more sampling effort than others, whereas some trophic links
(sometimes referred to as forbidden links) remain unobserved because of
biological constraints such as spatio-temporal uncoupling, size or
reward mismatching, foraging constraints and physiological-biochemical
constraints, which are irrespective of sufficient sampling effort
(Jordano, 2016). Previous studies such as Caron et al. (2022) and Gupta
et al. (2022) have shown that the predicted food webs from these models
usually have greater connectance than the observed ones. One solution to
compensate for undersampling is using a food web model such as the
Allometric Diet Breadth Model (ADBM) (Petchey et al., 2008) (reference
(gut content paper)) to predict the missing links and then measure the
robustness of the predicted food web. The ADBM is a mechanistic model
constructed using foraging rules based on the body sizes of prey and
predator, where trophic interactions satisfying those rules would be
predicted by the model, which are perhaps not observed because those
interactions are rare. However, this solution is not infallible, as it
is likely that the food web model might still miss some links and also
may predict some links that could not, in fact occur.

@@

The food webs were more robust to the random extinction scenario than
the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
and Benguela Pelagic food webs had more variations in robustness within
the model food webs as compared to the other food webs (Fig.
\ref{fig:fig_r4} (b)). Skipwith Pond and Broadstone Stream (taxonomic
aggregation) food webs were the most robust (Median \(R_{50} = 0.5\))
for both model and observed food webs. The food webs were more robust to
the random extinction scenario than the most connected scenario (Fig.
\ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had
more variations in robustness within the model food webs as compared to
the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond,
Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size
aggregation) food webs were the most robust (Median \(R_{50} = 0.5\))
for both model and observed food webs. Although there were few less
robust model food webs in the Broadstone Stream (size aggregation) as
shown by the outliers.

@@

\caption{\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. Some points are not visible due to perfect overlap in b and c. Refer to Fig. 7 in the Supplementary Information for a faceted visualisation. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\hypertarget{a-paragraph-on-the-implication-of-our-study}{%
\subsection{A paragraph on the implication of our
study}\label{a-paragraph-on-the-implication-of-our-study}}

\begin{itemize}
\tightlist
\item
  On the uncertainty in the ADBM estimates
\item
  On the limitation of a food web model
\item
  On undersampling
\end{itemize}

Our study also depicts that the uncertainty in the model predictions can
have a strong influence on the perceived robustness of the observed food
webs. The large variations in the robustness of the observed food webs
suggest why it is crucial to incorporate uncertainty in the food web
predictions. At the same time, our study also quantifies the impact of
undersampling on the perceived robustness of the observed food webs and
thus influencing the perceived functioning and stability of the food
webs (reference). This strongly suggest why it is crucial to incorporate
the influence of undersampling.

Contrary to general expectations (Dunne et al., 2002b), food web
robustness did not always increase with the connectance (Fig.
\ref{fig:fig_r5}). For example, the Benguela Pelagic and Small Reef ADBM
predicted food webs were surprisingly less robust to primary extinctions
on average in the least connected extinction scenario compared to the
observed food webs (Fig. \ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)).
In these two food webs, the extinction of the least connected species
could cause an almost complete, or complete collapse of the food web. We
suspect this is because the ADBM predicted food webs have a lower
proportion of basal species when compared to that of the observed food
webs (Fig: 6 (a) in Gupta et al. (2022)). As a result, these low-degree
basal species are the ones to be removed at an early stage in the
deletion sequence, thereby resulting in an earlier food web collapse in
the ADBM predicted food web as compared to that of the observed food web
(Fig: \ref{fig:fig_r3} (a) and (j)). This suggests that the greater
connectance predicted by the ADBM resulted in a more robust food web on
average. However, differences in the predicted food web properties, such
as a lower proportion of basal species and higher maximum trophic level
(Fig: \ref{fig:fig_a1}) when compared to that of the predicted food webs
counteracted that effect and led to reduced robustness. On average, a
consumer in a food web with a higher maximum trophic level would have
fewer resources and be more susceptible to extinction than a consumer in
a food web with a lower maximum trophic level (Binzer et al., 2011).
This suggests that food web properties other than connectance play an
important role in determining a food web's robustness and, therefore,
should also be taken into account (Binzer et al., 2011; Mendonça et al.,
2022; Riede et al., 2011).

@@

Since the ADBM predicted food webs have a lower proportion of basal
species and a higher maximum trophic level as compared to that of the
observed food webs (Fig: 6 (a) in Gupta et al. (2022) and Fig.
\ref{fig:fig_a1} in Supplementary Information), it would be interesting
to use these properties as summary statistics to parameterise the ADBM
and investigate how that influences the difference in the robustness
between the ADBM predicted and the observed food webs. We would expect a
more highly constrained predicted food web structure, lower variation in
robustness, and a greater apparent influence of connectance on
robustness.

@@

\hypertarget{supplementary-information}{%
\section{Supplementary Information}\label{supplementary-information}}

\begin{figure}[H]

{\centering \includegraphics[width=450px]{../results/plot_max_tl_ADBM_vs_emp}

\caption{\label{fig:fig_a1} The maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs. Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-4}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=450px]{../results/plot_R50_ADBM_vs_obs_ra_lc_facet}

\caption{\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

@@

>>>>

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Undersampling can lead to missing trophic interactions in recorded
  food webs, with potential consequences for the perceived functioning
  and stability of the food webs. Undersampling can be compensated for
  by using food web models such as the allometric diet breadth model
  (ADBM) to predict missing links. Simultaneously, models might predict
  links which cannot occur, i.e., real false positives.
\item
  Previous research shows that (i) food web robustness (the inverse of
  the number of secondary extinctions occurring due to primary
  extinctions) increases with connectance (the number of realised
  trophic links divided by the number of possible links), and (ii) that
  model predicted food webs usually have greater connectance than the
  observed ones. Thus, we expect that predicted food webs are more
  robust than the observed ones. However, this expectation has never, to
  our knowledge, been tested, nor has the effect size, i.e.~the
  difference in robustness of predicted and observed food web with
  respect to the difference in their connectance, been quantified.
\item
  We fill this research gap by comparing the robustness of observed food
  webs to the robustness of food webs predicted by a model (the ADBM)
  that can account for missing links. We did this for 12 different food
  webs from a wide variety of ecosystems. We used three extinction
  scenarios: random, most connected, and least connected.
\item
  We found, as expected, that the predicted food webs were more robust
  than the observed food webs, which can be attributed to the higher
  connectance of the predicted food webs. On average, for every one unit
  of increase in connectance, we found that the food webs robustness
  increased by 0.52 units for the most connected species extinction
  scenario and by 0.04 units for the random species extinction
  scenarios. On the other hand, we saw no effect or very little effect,
  on average, of increased connectance for the least connected species
  extinction scenario for all except two of the 12 food webs.
\item
  These results show that undersampling can lead to large underestimates
  of food web robustness that can be compensated for by filling in
  missing links with food web models. Also, the differences in the
  structural properties of the model predicted food webs and the
  observed food webs suggest structural properties of a food web could
  be used as summary statistics to fit models such as the ADBM to the
  observed data.
\end{enumerate}
\end{abstract}

@@

@@

A key assumption of the observed food webs is that they are very well
sampled, i.e.~all the links that in reality can occur are represented.
However, it is known that not all food webs are very well sampled and do
not represent all of the feeding links that can occur (Caron et al.,
2022; Jordano, 2016; Patonai \& Jord'an, 2017). Some rare trophic links
require more sampling effort than others, whereas some trophic links
(sometimes referred to as forbidden links) remain unobserved because of
biological constraints such as spatio-temporal uncoupling, size or
reward mismatching, foraging constraints and physiological-biochemical
constraints, which are irrespective of sufficient sampling effort
(Jordano, 2016). Previous studies such as Caron et al. (2022) and Gupta
et al. (2022) have shown that the predicted food webs from these models
usually have greater connectance than the observed ones. One solution to
compensate for undersampling is using a food web model such as the
Allometric Diet Breadth Model (ADBM) (Gupta et al., 2023; Petchey et
al., 2008) to predict the missing links and then measure the robustness
of the predicted food web. The ADBM is a mechanistic model constructed
using foraging rules based on the body sizes of prey and predator, where
trophic interactions satisfying those rules would be predicted by the
model, which are perhaps not observed because those interactions are
rare. However, this solution is not infallible, as it is likely that the
food web model might still miss some links and also may predict some
links that could not, in fact occur.

@@

The food webs were more robust to the random extinction scenario than
the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
and Benguela Pelagic food webs had more variations in robustness within
the model food webs as compared to the other food webs (Fig.
\ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic
aggregation) and Broadstone Stream (size aggregation) food webs were the
most robust (Median \(R_{50} = 0.5\)) for both model and observed food
webs (Fig. \ref{fig:fig_r4} (b)). Although there were few less robust
model food webs in the Broadstone Stream (size aggregation) as shown by
the outliers.

@@

\caption{\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. Some points are not visible due to perfect overlap in b and c. Refer to Fig. S3 in the Supplementary Information for a faceted visualisation. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-2}
\end{figure}

@@

Our study also depicts that the uncertainty in the model predictions can
have a strong influence on the perceived robustness of the observed food
webs. The large variations in the robustness of the model predicted food
webs suggest why it is crucial to incorporate uncertainty in the food
web predictions. At the same time, our study also quantifies the impact
of undersampling on the perceived robustness of the observed food webs
which then influences the perceived functioning and stability of the
food webs (Dunne et al., 2002a; Thompson et al., 2012). This strongly
suggest why it is crucial to incorporate the influence of undersampling.

Contrary to general expectations (Dunne et al., 2002b), food web
robustness did not always increase with the connectance (Fig.
\ref{fig:fig_r5}). For example, the Benguela Pelagic and Small Reef ADBM
predicted food webs were surprisingly less robust to primary extinctions
on average in the least connected extinction scenario compared to the
observed food webs (Fig. \ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)).
In these two food webs, the extinction of the least connected species
could cause an almost complete, or complete collapse of the food web. We
suspect this is because the ADBM predicted food webs have a lower
proportion of basal species when compared to that of the observed food
webs (Fig. 6 (a) in Gupta et al. (2022)). As a result, these low-degree
basal species are the ones to be removed at an early stage in the
deletion sequence, thereby resulting in an earlier food web collapse in
the ADBM predicted food web as compared to that of the observed food web
(Fig. S1 (a) and (j) in the Supplementary Information). This suggests
that the greater connectance predicted by the ADBM resulted in a more
robust food web on average. However, differences in the predicted food
web properties, such as a lower proportion of basal species (Fig. 6 (a)
in Gupta et al. (2022)) and higher maximum trophic level (Fig. S2 in the
Supplementary Information) when compared to that of the predicted food
webs counteracted that effect and led to reduced robustness. On average,
a consumer in a food web with a higher maximum trophic level would have
fewer resources and be more susceptible to extinction than a consumer in
a food web with a lower maximum trophic level (Binzer et al., 2011).
This suggests that food web properties other than connectance play an
important role in determining a food web's robustness and, therefore,
should also be taken into account (Binzer et al., 2011; Mendonça et al.,
2022; Riede et al., 2011).

@@

Since the ADBM predicted food webs have a lower proportion of basal
species and a higher maximum trophic level as compared to that of the
observed food webs (Fig. 6 (a) in Gupta et al. (2022) and Fig. S2 in the
Supplementary Information), it would be interesting to use these
properties as summary statistics to parameterise the ADBM and
investigate how that influences the difference in the robustness between
the ADBM predicted and the observed food webs. We would expect a more
highly constrained predicted food web structure, lower variation in
robustness, and a greater apparent influence of connectance on
robustness.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-gupta2023many}{}}%
Gupta, A., Figueroa, D., O'Gorman, E., Jones, I., Woodward, G., \&
Petchey, O. L. (2023). How many predator guts are required to predict
trophic interactions? \emph{Food Webs}, \emph{34}, e00269.

@@

\leavevmode\vadjust pre{\hypertarget{ref-thompson2012food}{}}%
Thompson, R. M., Brose, U., Dunne, J. A., Hall, R. O., Hladyz, S.,
Kitching, R. L., Martinez, N. D., Rantala, H., Romanuk, T. N., Stouffer,
D. B., et al. (2012). Food webs: Reconciling the structure and function
of biodiversity. \emph{Trends in Ecology \& Evolution}, \emph{27}(12),
689--697.
